Think deep for reef resilience

### 2025-09-10 paper/paper_draft.qmd
Add citation for thermal stress advancement, and placeholder for connectivity citation

Recent advances in whole-ecosystem larval connectivity modelling and coral thermal response
research enable integrated investigation of how these multiple factors interact to determine
climate resilience. By incorporating the latest coral population models
[@ribeirodealmeida2024], ecosystem-wide connectivity data, and updated climate projections
[@dixon2022], we can examine which factors most strongly influence reef persistence under
different scenarios. While connectivity has been emphasized as critical for GBR resilience
[@hock2017], and remains an important consideration, our integrated modelling reveals depth
may play a fundamental role in determining maintenance of reef coral populations and
positive carbonate budgets under current projections of climate change.

>>>>

Recent advances in whole-ecosystem larval connectivity modelling **\[Insert GBR1
connectivity citation.\]** and coral thermal response research [@bairos-novak2021] enable
integrated investigation of how multiple factors interact to determine climate resilience.
By incorporating the latest coral population models [@ribeirodealmeida2024], ecosystem-wide
connectivity data, and updated climate projections [@dixon2022], we can examine which
factors most strongly influence reef persistence under different scenarios. While
connectivity has been emphasized as critical for GBR resilience [@hock2017], and remains an
important consideration, our integrated modelling reveals depth may play a fundamental role
in determining maintenance of reef coral populations and positive carbonate budgets under
current projections of climate change.
